---
title: "AS-B1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading libraries 

We will start by loading the necessary libraries for this assignment 

```{r}
library(dplyr) 
library(tidyverse)
library(datateachr) # this provides the dataset used to test our functions 
library(testthat) # this is used to test our functions
```

# Making a Function and Documenting
This function will return the difference of the average height (per sex) to an inputed height (in cm).

```{r}
#' @tite Average Height Difference Function 
#'  
#' @description The `Avg_height_diff` function calculates the absolute difference of the average adult height per sex (178.1 cm for Canadian men & 164.7 cm for Canadian women) to an inputted height (in cm).
#'  
#'
#' @param height Height of person (in cm). I named this paramater as height because that is name the input. 
#' @param male Variable to indicate the sex of the inputted height. I named this paramater as male because that corresponds to the input. 
#'
#' @return Absolute value of the difference of the average height and the inputted height (in cm)
#' 
#'
#' @examples 
#' Avg_height_diff(181, male = TRUE)
#' Avg_height_diff(114, male = FALSE)
#' 
Avg_height_diff <- function(height, male = TRUE){
  if(!is.numeric(height)) { 
    stop('This function only works for numeric input!\n',
         'You have provided an object of class: ', class(height)[1])
  }
  if(is.na(height)) { 
    stop('This function only works for numeric input!\n',
         'You have provided an NA value ')
  }
  if(male == TRUE) {
    result <- abs(178.1 - height)
    paste("With the average Canadian male height at 178.1 cm, you are", round(result, 2), "cm different than the average.")
  } else {
    result2 <- abs(164.7 - height)
    paste("With the average Canadian female height at 164.7 cm, you are", round(result2, 2),  "cm different than the average.")
  }
}

```

# Function Examples 
```{r, error = TRUE}

# We can see that inputting the same number will provide different answers depending on the sex
Avg_height_diff(160, male = TRUE)
Avg_height_diff(160, male = FALSE)


# Attempting to input non-numeric values will return an error
Avg_height_diff("cow", male = TRUE)

```

# Testing the function 
Now we can use the `testthat` package to run some tests on the function to ensure it works. 
We will be using the *cancer_sample* and *apt_buildings* dataset from the `datateachr` package. 
```{r}
print(cancer_sample)
print(apt_buildings)
```





## Test 1
Our first test checks to see if an error message will be displayed when a non-numeric variable is used for the *height* parameter. We will be using the *diagnosis* column from the *cancer_sample* dataset as our non-numeric variable.
```{r}
test_that("Function shows an error if non-numerical value is used as the height", {
  expect_error(Avg_height_diff(cancer_sample$diagnosis, male= FALSE))
})
```

## Test 2 
Our second test checks to see if an error message will be displayed when an NA value is used for the *height* parameter. We will be using *row 6* of the *no_barrier_free_accessible_units* column from the *apt_buildings* dataset to extract an NA value. 
```{r}
test_that("Function shows an error if NA value is used as the height", {
  expect_error(Avg_height_diff(apt_buildings$no_barrier_free_accessible_units[6], male = TRUE))
})
```

## Test 3 
Our final test will ensure that the class for a given singular output is a *character*. We will be using *row 1* of the *radius_mean* column from the *cancer_sample* dataset to extract a *charachter* output. 
```{r}
test_that("Function produces a output with a charachter class type", {
  expect_true(is.character(Avg_height_diff(cancer_sample$radius_mean[1], male = TRUE)))
})
```
