---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ASB2

<!-- badges: start -->
<!-- badges: end -->

The goal of ASB2 is to provide information regarding the average adult height (per sex) and compare it to inputted heights. This package contains a function which displays the average adult height (for the selected sex) and calculates the absolute difference between it and an inputted height (in cm)

## Installation

You can install the development version of ASB2 like so:

``` r
devtools::install_github("Dilan330/assignment-b1-and-b2-Dilan330, ref="0.1.0")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ASB2)

## Finding the absolute difference between the Canadian average height for a male and an inputted height (160 cm)
Avg_height_diff(160, male = TRUE)
```
